Automated Verification and Synthesis of Embedded \& Cyber-Physical Systems: Advances and Challenges

### 2018-03-10 paper.tex
initial mods to challenges and research problems

The goals of the present article is to briefly present part of the established research and also clarify current trends, which are mainly driven by ECPSs, IoT, and ML. We present a brief discussion about models for ECPSs, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, counterexample guided inductive synthesis, and system model incorporation, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding verification and synthesis of embedded systems are described, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section~\ref{achievements} then describes current achievements and future trends in verification and synthesis of ECPSs and Section \ref{Newapp} addresses new applications, which take into account the new trends ({\it e.g.}, ML) mentioned here. Finally, we conclude and describe future work, in Section~\ref{conclusions}.

@@

\begin{prf}\label{interpolants}
\begin{definition}\label{interpolants}
\textit{\textcolor{blue}{Given a pair of formulae $\left(A,B\right)$, such that $A \wedge B$ is inconsistent, and a proof by resolution for $\left(A,B\right)$, an \textit{interpolant} for $\left(A,B\right)$ is a formula $F$ with the following properties}~\cite{McMillan03,McMillan05}: }

@@

In particular, the main challenges regarding verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning state-space exploration during verification, providing completeness, {\it i.e.},  if all possible states can be reached and evaluated, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as:
%
\begin{enumerate}
	\item Time and energy constraints;
	\item Handling of concurrent software;
	\item Platform restrictions;
	\item Verification of code pieces or modules that rely on larger structures;
	\item Legacy designs; %, which are usually developed with low-level languages.
	\item Support to different programming languages, frameworks, and interfaces;
	\item Correct code instrumentation;
	\item Handling of non-linear and non-convex optimization problems;
	\item Incorporation of new and adapted checks, due to system or environment evolution.
\end{enumerate}

@@

The sixth aspect is related to evolving development processes and technologies, which may delay the application of suitable verification and synthesis approaches, if verifiers and synthesizers do not support different programming languages and interfaces. The seventh aspect highlights a subjective task in verification: where one must insert an evaluation point or assertion, in order to correct address a property. The eighth one is related to the widespread use of embedded systems in autonomous-vehicle navigation systems~\cite{Adouane16}, which demands optimization solving during their execution for a wide range of functions, including non-linear and non-convex problems using fixed- and floating-point arithmetic.

@@

Those nine challenges place additional difficulties for developing reliable synthesizers for embedded systems, especially for cyber-physical systems and micro-grids, where controlled objects ({\it e.g.}, physical plants) typically exhibit continuous behavior (which may eventually change), whereas controllers (usually implemented by real-time computer systems) operate in discrete time and over a quantized domain. In particular, synthesizers for those systems need to consider the effects of quantizers (A/D and D/A converters), when a digital equivalent of the controlled object is considered, {\it i.e.}, a model of their physical environment (cf. intelligent product in Figure~\ref{intelligent-product}). Additionally,  finite-precision arithmetic and their related rounding errors need to be considered, when correct-by-construction code is generated for ECPS.

%--------------------------------------
\section{Research Problem (RP)}
\label{Research-Problem}
%--------------------------------------

This survey tackles seven major problems in computer-aided verification and synthesis for ECPS, which are (partially) open in current published research.

@@

Section~\ref{achievements} outlines contributions toward such research problems.

@@

@@

Given that software complexity has significantly increased in ECPS, there are still some (recent) advances to stress and exhaustively cover the system state space, in order to verify low-level properties that have to meet the application's deadline, access memory regions, handle concurrency, and control hardware registers. There is a trend towards incorporating knowledge about the system to be verified, which may take software verification and synthesis one step further, where not only code correctness will be addressed, but also full system reliability. In addition, it seems interesting to provide behavioral models when new application interfaces or programming language features are used, in order to extend capabilities of current verification tools, without changing the core BMC module. Finally, there are some bottlenecks in software verification that are possible to be handled with machine learning, given some initial studies carried out in the current literature, which may represent another step towards a unified and complete approach that combines code verification, behavior correctness, environment adaptation, and system evolution.

As future work, the main goal of this research is to extend BMC as a design, verification, and synthesis tool for achieving correct-by-construction ECPS implementations. Special attention will be given to modern micro-grids, considering small-scale versions of a distributed system, so that reliability and other system-level properties ({\it e.g.}, carbon emission reduction in smart cities) are amenable to automated verification and synthesis, probably through behavior models. Additionally, ML techniques will be incorporated to BMC frameworks, in order to provide flexibility and specific-problem tuning.

>>>>

The goals of the present article is to briefly present part of the established research and also clarify current trends, which are mainly driven by ECPSs, IoT, and ML. We present a brief discussion about models for ECPSs, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, counterexample guided inductive synthesis, and system model incorporation, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding verification and synthesis of embedded systems are described, while Section~\ref{achievements} tackles those challenges that are (partially) open in current published research and later describes current achievements and future trends in verification and synthesis of ECPSs, and Section \ref{Newapp} addresses new applications, which take into account the new trends ({\it e.g.}, ML) mentioned here. Finally, we conclude and describe future work, in Section~\ref{conclusions}.

@@

\begin{prf}
\begin{definition}\label{interpolants}
\textit{\textcolor{blue}{Given a pair of formulae $\left(A,B\right)$, such that $A \wedge B$ is inconsistent, and a proof by resolution for $\left(A,B\right)$, an \textit{interpolant} for $\left(A,B\right)$ is a formula $F$ with the following properties}~\cite{McMillan03,McMillan05}: }

@@

In particular, the main challenges regarding verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning state-space exploration during verification, providing completeness, {\it i.e.},  if all possible states can be reached and evaluated, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as:
%
\begin{enumerate}
	\item Time and energy constraints;
	\item Handling of concurrent software;
	\item Platform restrictions;
	\item Verification of code pieces or modules that rely on larger structures;
	\item Legacy designs; %, which are usually developed with low-level languages.
	\item Support to different programming languages, frameworks, and interfaces;
	\item Correct code instrumentation;
	\item Handling of non-linear and non-convex optimization problems;
	\item Incorporation of new and adapted checks, due to system or environment change;
	\item \textcolor{blue}{Provide a form of system evolution, in such a way that a version more adapted to the current scenario is obtained.}
\end{enumerate}

@@

The sixth aspect is related to evolving development processes and technologies, which may delay the application of suitable verification and synthesis approaches, if verifiers and synthesizers do not support different programming languages and interfaces. The seventh aspect highlights a subjective task in verification: where one must insert an evaluation point or assertion, in order to correctly address a property. The eighth one is related to the widespread use of embedded systems in autonomous-vehicle navigation systems~\cite{Adouane16}, which demands optimization solving during their execution for a wide range of functions, including non-linear and non-convex problems using fixed- and floating-point arithmetic.

@@

\textcolor{blue}{The tenth aspect is related to the current development and test strategies adopted for embedded systems, which aim at simply providing robust structures, instead of antifragile ones. In summary, it is not feasible to account for every scenario or error, but it would be more interesting to provide a module or structure capable of thriving on problems and getting more robust. Such an aspect shares some similarity with the ninth one and may also be achieved through ML techniques.}

Those ten challenges place additional difficulties for developing reliable synthesizers for embedded systems, especially for cyber-physical systems and micro-grids, where controlled objects ({\it e.g.}, physical plants) typically exhibit continuous behavior (which may eventually change), whereas controllers (usually implemented by real-time computer systems) operate in discrete time and over a quantized domain. In particular, synthesizers for those systems need to consider the effects of quantizers (A/D and D/A converters), when a digital equivalent of the controlled object is considered, {\it i.e.}, a model of their physical environment (cf. intelligent product in Figure~\ref{intelligent-product}). Additionally,  finite-precision arithmetic and their related rounding errors need to be considered, when correct-by-construction code is generated for ECPS.

\textcolor{blue}{In the preceding sections, we identified and discussed many aspects regarding ECPSs, which included design, synthesis, behavior, verification, and bottlenecks. Nonetheless, from the point of view of computer-aided verification and synthesis for ECPS, it is possible to highlight seven major problems, which are tackled here and can be regarded as (partially) open in current published research.}

@@

\textcolor{blue}{Due to the fact that the mentioned research problems are the focus of the present technology area, many works tackled them and other researchers still address them. As a consequence, we can cite the followinf contributions toward them.}

@@

\textcolor{blue}{In addition, a aspect closely related to ML techiniques, as mentioned in Section \cite{Verification-Challenges}, is system fragility. Currently, most design strategies try to produce robust systems, which are able to deal with a limited set of common errors that happen when they are operating, {\it i.e., they are robust}. Nonetheless, that is effective only if problems foreseen during design phases happen; otherwise, operation may be compromised.}

\textcolor{blue}{Indeed, depending on the employed point of view, fragility and robustness may be regarded as the same property. A system that is more robust is less fragile, but it is still prone to problems, which depends on operating scenarios, use cases, and uncertainties. 
In summary, if the chosen model does not tackle every possible problem or error that might occur in a given environment, system-failure events are still possible, which is true even for the Ariane 5's failure \cite{antifragile}.}

\textcolor{blue}{As a result, it may be more interesting to develop methodologies that are not simply robust, regarding a predetermined condition, but instead thrive on problems and grow stronger (as the human body, which gets stronger when exposed to germs), which leads to antifragile systems. In engineering, we are only beginning to develop solutions that can be classified as antifragile, such as multiple-input/multiple-output (MIMO) systems, which use multiple signal copies together with multipath to achieve performance enhancement~\cite{spectrum2013}.}

\textcolor{blue}{Systems that could greatly benefit from being antifragile are the cyber-physical ones, which interact with other external systems and use their internal representations to interpret physical properties. As faults occur, which may be treated with some sort of system elasticity, and external environments are normally dynamic, given that it naturally changes with time, variations in operating conditions happen and should be tolerated, in order to keep behavior quality \cite{antifragile}. Besides, when discussing the fundamentals of antifragility, it is difficult not to tackle machine learning \cite{antifragile}, which has the potential to provide some wisdom regarding correct behavior and internal representations, in order to keep a system working in a volatile environment.}

\textcolor{blue}{For instance, we could think about a system including an adaptation module composed by two elements: a machine learning engine, capable of capturing current behaviors and identify different trens, and a SMT-based verification method, capable of recursively performing retuning procedures, which could test new parameters suggested by the machine learning module and then judge theis suitability. As a consequence, we would be able to design systems with the potential to being antifragile, given that they would learn from new challenges and then modify its behavior model, in order to account for new errors and threats.}

@@

Given that software complexity has significantly increased in ECPS, there are still some (recent) advances to stress and exhaustively cover system state space, in order to verify low-level properties that have to meet the application's deadline, access memory regions, handle concurrency, and control hardware registers. There is a trend towards incorporating knowledge about the system to be verified, which may take software verification and synthesis one step further, where not only code correctness will be addressed, but also full system reliability. In addition, it seems interesting to provide behavioral models when new application interfaces or programming language features are used, in order to extend capabilities of current verification tools, without changing the core BMC module. Finally, there are some bottlenecks in software verification that are possible to be handled with machine learning, given some initial studies carried out in the current literature, which may represent another step towards a unified and complete approach that combines code verification, behavior correctness, environment adaptation, and system evolution.

As future work, the main goal of this research is to extend BMC as a design, verification, and synthesis tool for achieving correct-by-construction ECPS implementations. Special attention will be given to modern micro-grids, considering small-scale versions of a distributed system, so that reliability and other system-level properties ({\it e.g.}, carbon emission reduction in smart cities) are amenable to automated verification and synthesis, probably through behavior models. Additionally, ML techniques will be incorporated to BMC frameworks, in order to provide flexibility and specific-problem tuning, or even allow system adaptation and behavior tuning.
